---
title: "ISA401 Final"
author: "Rylee Elling"
date: "2026-04-29"
output: html_document
---

## INFO ABOUT WHAT THIS PROJECT IS


```{r}
chat <- ellmer::chat_openai(
  model = "gpt-5-mini-2025-08-07"
)

usethis::edit_r_environ(scope = "project")

```


# Import libraries used in the project

```{r}
library(tidyverse)
library(dplyr)
library(purrr)
library(readr)
```


## Scraping and Cleaning Insider Monkey Revenue Data

```{r - Insider Monkey Revenue}


# Use the ellmer package to read the Statista bar chart of the revenue of streaming services, saved as a PNG file. 
# Scrape from this image the name of each streaming platform as a string and the revenue as listed in the bar chart as decimal.


# Verify that the Hollywood Reporter site allows web scraping for the path we wish to scrape
# A TRUE result allows web scraping

robotstxt::paths_allowed(
  paths = "/business/business-news/streaming-profit-report-netflix-leads-disney-warner-bros-1236184451/",
  domain = "https://www.hollywoodreporter.com"
)


# Insider Monkey has ranked the top 15 streaming sites and included each sites' revenue. These are spread across 6 different pages


# Start with the bottom 10 ranked sites
# read the html of the site into a variable

hreporter_webpage_top15 <- rvest::read_html("https://www.insidermonkey.com/blog/15-biggest-streaming-and-tv-companies-in-the-us-1192787/")

# Pull the platform names from the website using rvest and the associated html elements

hreporter_webpage_top15 |>
  rvest::html_elements("#post-1192787 > div.clearfix > div > h3 > b") |>
  rvest::html_text() -> rev_10

# convert the text that was scraped into a tibble
platforms_10 <- tibble(Platform = rev_10)

# Clean the tibble by removing the empty row
platforms_10 <- platforms_10[-3, ]


# Pull the revenues from the website
hreporter_webpage_top15 |>  
  rvest::html_elements("div > p > b > i") |> rvest::html_text() -> rev_val_10

# convert the scraped text into a tibble and clean by removing the empty row
rev_10 <- tibble(Revenue = rev_val_10)
rev_10 <- rev_10[-4, ]

# combine the tibbles into one data frame that now contains the name and revenue of 10/15 of the top performing streaming sites
# bot_10_revs <- data.frame(platforms_10, rev_10)
revenues <- data.frame(platforms_10, rev_10)



# The 5th ranked streaming site

# read the html of the site into a variable
hreporter_webpage_top5 <- rvest::read_html("https://www.insidermonkey.com/blog/5-biggest-streaming-and-tv-companies-in-the-us-1192786/")

# scrape the platform name
hreporter_webpage_top5 |>
  rvest::html_elements("div.clearfix > div > h3 > b") |>
  rvest::html_text() -> Platform

# scrape the revenue
hreporter_webpage_top5 |>  
  rvest::html_elements("div > p > b > i") |> rvest::html_text() -> Revenue

# create a data frame for the 5th ranked platform and its revenue
df <- data.frame(Platform, Revenue)

# combine the dataframes together to get 11/15 of the sites
# bot_10_revs <- rbind(bot_10_revs, df)
revenues <- rbind(revenues, df)

# Function to scrape the remaining 4 pages

# use the page number from a list below to scrape the corresponding page of the remaining platform names and revenue
scrape_monkey <- function(page){
  url <- paste0("https://www.insidermonkey.com/blog/5-biggest-streaming-and-tv-companies-in-the-us-1192786/", page, "/") 
  hreporter_webpage <- rvest::read_html(url)
  Sys.sleep(2)
  
  # scrape the webpage for the platform name
  hreporter_webpage |>
  rvest::html_elements("div.clearfix > div > h3 > b") |>
  rvest::html_text() -> platform
  
  # scrape the webpage for the revenue
  hreporter_webpage |>  
  rvest::html_elements("div > p > b > i") |> rvest::html_text() -> rev

  # put these values into a dataframe, to be returned and combined into the final datframe
  df <- data.frame(Platform = platform, Revenue = rev)
  
  Sys.sleep(2) #2 seconds
  
  return(df)
  
}

# page numbers of the remaining pages needed to be scraped
pages <- c('5','4','3','2')

# loop through the remaining 4 pages and add the names and revenues to complete the dataframe
for (nums in pages){
  df = scrape_monkey(page = nums)
  head(df)
  revenues <- rbind(revenues, df)
}


rev_prompt <- revenues
# Prompts to clean platform names and revenues by removing the bullet point numbers and "Estimated 2022 Revenue: $" and "billion" from the revenues
platform_revenue <- ellmer::type_object( 
  `Platform` = ellmer::type_string(
    description = "The streaming platform name. Write each platform name as a new row. There must be 15 total rows.
Rules:
1. If the text is written as 'numeric.'X. Y', write Y
2. If the text contains (NYSE:, follow the example below.
Examples:
- '2. Amazon Prime Video' → Amazon Prime Video
- '14. fuboTV Inc. (NYSE:' → fuboTV Inc.
- '3. Disney+ ' → Disney+
"
  )
,
`2022 Revenue (billions)` = ellmer::type_number(
    description = "Extract the share of total tv viewing. Write each revenue value as a new row. There should be 15 total rows.
Rules:
1. If the text contains Estimated 2022 Revenue: $X billion, write X
2. If the text contains 2022 Revenue: $Y billion, write Y
Examples:
- '2022 Revenue: $1 billion' → 1
- 'Estimated 2022 Revenue: $2.6 billion' → 2.6
"
  )
)


# Clean the revenues data using the prompts above
revenue <- ellmer::parallel_chat_structured(chat, rev_prompt, type = ellmer::type_array(platform_revenue)) 

# collect the cleaned platform names and revenues 
revenue <- cbind(revenue[[1]], revenue[[2]])

# # remove the unrelated and redundant columns
revenue <- revenue[, -2]
revenue <- revenue[, -2]

```


## Scraping Brandience subscription OTT video viewers Data

```{r - Brandience subscription OTT video viewers}

# Use the ellmer package to read the Brandience bar chart of the subscription OTT video viewers in the US by streaming service provider, saved as a PNG file. 

# Scrape from this image the name of each streaming platform as a string and the OTT as listed in the bar chart as decimal.

ott <- chat$chat_structured(
  ellmer::content_image_file("../Data/project_images/brandience_OTT_views.png"),
  type = ellmer::type_array(ellmer::type_object(
    Platform = ellmer::type_string(
      description = "The name of each of the 12 streaming services listed in the bar chart. Separate each service into a new row. EX: Disney+"
    ),
    `Subscription OTT Video Viewers (Millions)` = ellmer::type_number(
      description = "The video viewers for the streaming service from 2024-2028. Listed in the bar chart right of the blue bar. Separate each revenue into a new row.  EX: 184.2"
    )
  )
))

```



## Scraping Emarketer Top platforms by ad spending data

```{r - Emarketer Top platforms by ad spending}

# Use the ellmer package to read the Emarketer table of the Top 10 Streaming TV Platforms Ranked by Ad Spending, saved as a PNG file. 

# Scrape from this image the name of each streaming platform as a string, the ad spend in 2024 as an integer, the ad spend in 2025 as an integer, and the % change as a decimal.

# Since the table does not have a 2024, 2025, and % change for each column, the corresponding values are not required to be scraped by the AI.

ad_spend <- chat$chat_structured(
  ellmer::content_image_file("../Data/project_images/adtechradar_ad_spending.png"),
  type = ellmer::type_array(ellmer::type_object(
    Platform = ellmer::type_string(
      description = "The name of each of the 10 streaming services listed in the chart. Separate each service into a new row. EX: Disney+"
    ),
    `2024 Ad Spending (Millions)` = ellmer::type_integer(
      description = "The ad spend for the streaming service from 2024 and 2025. Listed in the  chart under the 2024 column name, to the right of each service. Separate each revenue into a new row.  EX: 4386",
    required = FALSE
    ), 
    `2025 Ad Spending (Millions)` = ellmer::type_integer(
      description = "The ad spend for the streaming service from 2024 and 2025. Listed in the  chart under the 2025 column name, to the right of each service. Separate each revenue into a new row. EX: 4690",
    required = FALSE
    ),
    `Ad Spending % Change` = ellmer::type_number(
      description = "The change in ad spending from 2025 to 2024 for each streaming service. Listed in the chart under the % change column. Change the percentage to a decimal EX: 7% = 0.07", required = FALSE
    )
  )
))


```

## Scraping and Cleaning CAGR over time data from Statista

```{r Statista CAGR over Time}

# Use the ellmer package to read the Statista bar chart of the Compound Annual Growth Rate over time for varying streaming services. 

# Scrape from this image the name of each streaming platform as a string and the CAGR as listed in the bar chart as decimal.


CAGR <- chat$chat_structured(
  ellmer::content_image_file("../Data/project_images/statista_CAGR_overT.png"),
  type = ellmer::type_array(ellmer::type_object(
    Platform = ellmer::type_string(
      description = "The name of each of the 6 streaming services listed in the bar chart. Separate each service into a new row. EX: Paramount+"
    ),
    `Compound Annual Growth Rate (CAGR) (%)` = ellmer::type_number(
      description = "The CAGR for the streaming service. Listed in the bar chart above the blue bar. Separate each revenue into a new row. Write this number without the percent symbol. Change the percentage to a decimal EX: 37% = 0.37"
    )
  )
))

```


## Scraping watch time data from Statista

```{r Statista Watch Time}


# Use the ellmer package to read the Statista double bar chart of the watch times for active users and total adults for varying streaming services. 

# Scrape from this image the name of each streaming platform as a string, the watch time of active users as an integer, and the watch time of the total adults as an integer.


watch_time <- chat$chat_structured(
  ellmer::content_image_file("../Data/project_images/statistia_watch_time.png"),
  type = ellmer::type_array(ellmer::type_object(
    Platform = ellmer::type_string(
      description = "The name of each of the 6 streaming services listed in the bar chart. Separate each service into a new row. EX: Disney+"
    ),
    `Active Users Average Daily Watch Time (minutes)` = ellmer::type_integer(
      description = "The time spent in minutes the avg daily viewer watches for each platform. Listed above the left most blue bar charts of each pair. Separate each into a new row.  EX: 63"
    ),
    
    `Total Adults Average Daily Watch Time (minutes)` = ellmer::type_integer(
      description = "The time spent in minutes the avg daily viewer watches for each platform. Listed above the right most dark bar charts of each pair. Separate each into a new row.  EX: 36"
    )
  )
))

```


## Scraping and Cleaning Ad break data from Streamable 

```{r}

# Verify that the Streamable site allows web scraping for the path we wish to scrape
# A TRUE result allows web scraping

robotstxt::paths_allowed(
  paths = "/how-many-ads-does-each-streaming-service-show",
  domain = "https://thestreamable.com"
)

# read the html of the site into a variable

streamable_webpage <- rvest::read_html("https://thestreamable.com/how-many-ads-does-each-streaming-service-show")

# scrape all tables on the site by reading the related html elements into a table

streamable_webpage |>
  rvest::html_elements("#content > article > div.markdown-body.width-fit.draft-current-text > table") |>
  rvest::html_table() -> all_tables

# The table created includes rows that hold a tibble of number of breaks per tv or movie, tibble of ad break length for tv or movie, tibble of ads per tv or movie, and tibble of whether ads are presented on kids material. 

# Join all of the rows in the table into one large table by joining on Streamer (platform name) and Original Article (unrelated link that is not needed)

# Begin by joining the tibble stored as an element of each list-column of the first two rows (The table created includes columns that hold the table of number of breaks per tv or movie and the ad break length for tv or movie)

big_table = dplyr::left_join(all_tables[[1]], all_tables[[2]], by = c('Streamer', 'Original Article'))

# Repeat for the remaining row, choosing not to include the tibble related to whether ads are presented on kids material. 

big_table = dplyr::left_join(big_table, all_tables[[3]], by = c('Streamer', 'Original Article'))


# remove the column containing information about the original article

big_table <- big_table |> dplyr::select(-`Original Article`)

# rename the Streamer column to be Platform to match other dataframes
big_table <- big_table |> rename(Platform = Streamer)

# store the second column of the dataframe as a list in prompts to be used with ellmer below
# this list will contain information about the breaks per 30 minute episode
big_table[[2]] |> as.list() -> prompts

# prompts for the chat to follow to separate the data into 3 columns: Whether the streaming service has ads during the pre-roll, the minumum number of breaks during an episode, and the maximum number of breaks
ep_breaks <- ellmer::type_object( 
  `Pre-roll breaks per 30 min episode` = ellmer::type_string( 
    description = "Whether the streaming service has ads during the pre-roll or not. EX: No pre-roll "
  ),
  `Minimum breaks per 30 min episode` = ellmer::type_integer( 
    description = "The minimum number of breaks during an episode. Represented in the list as number to number breaks during. Pick the smaller number. EX: 2"
  ),
  `Maximum breaks per 30 min episode` = ellmer::type_integer( 
    description = "The maximum number of breaks during an episode. Represented in the list as number to number breaks during. Pick the larger number. EX: 6", required = FALSE
  )
)

# use the prompts and prompted list to clean the data 
# store in a new data frame table 
ep_breaks_extracted <- ellmer::parallel_chat_structured(chat, prompts, type = ep_breaks) 


```


```{r Movie Breaks}

# store the third column of the dataframe as a list in prompts to be used with ellmer below
# this list will contain information about the breaks per movie

big_table[[3]] |> as.list() -> prompts

# prompts for the chat to follow to separate the data into 3 columns: Whether the streaming service has ads during the pre-roll, the minumum number of breaks during a movie, and the maximum number of breaks
mov_breaks <- ellmer::type_object(
  `Pre-roll breaks per movie` = ellmer::type_string( 
    description = "Extract whether the text contains 'Pre-roll' or 'No pre-roll'.
Rules:
- If the text contains 'No pre-roll', output 'No pre-roll'.
- If the text contains 'Pre-roll', output 'Pre-roll'.
- If both appear, output 'Pre-roll'.
- Ignore all other text."
  ),
  `Minimum breaks per movie` = ellmer::type_integer( 
    description = "Extract the minimum number of breaks during the movie.
Rules:
1. If the text contains 'mid-playback break', set minimum = 0.
2. If the text contains 'long pre-roll break' and no other numbers, set minimum = 0.
3. If the text contains a numeric range 'X to Y breaks', set minimum = X.
4. If the text contains a single number 'X breaks', set minimum = X.
5. If no number appears, return NA.
Examples:
- 'Pre-roll, 6 to 9 breaks during' → 6
- '1 long pre-roll break' → 0
- '1 long pre-roll break or mid-playback break' → 0
- 'Pre-roll, during' → NA", required = FALSE
  ),
  `Maximum breaks per movie` = ellmer::type_integer( 
    description = "Extract the maximum number of breaks during the movie.
Rules:
1. If the text contains 'mid-playback break', set maximum = 1.
2. If the text contains 'long pre-roll break' and no other numbers, set maximum = 0.
3. If the text contains a numeric range 'X to Y breaks', set maximum = Y.
4. If the text contains a single number 'X breaks', set maximum = X.
5. If no number appears, return NA.
Examples:
- 'Pre-roll, 6 to 9 breaks during' → 9
- '1 long pre-roll break' → 0
- '1 long pre-roll break or mid-playback break' → 1
- 'Pre-roll, during' → NA", required = FALSE
  )
)

# use the prompts and prompted list to clean the data 
# store in a new data frame table 
mov_breaks_extracted <- ellmer::parallel_chat_structured(chat, prompts, type = mov_breaks) 

```


```{r Ad break lengths}

# store the fourth column of the dataframe as a list in prompts to be used with ellmer below
# this list will contain information about the ad break length per episode
big_table[[4]] |> as.list() -> prompts_tv_len


# prompts for the chat to follow to separate the data into 2 columns: the minimum length of breaks during an episode, and the maximum length in seconds
ad_break_length_tv <- ellmer::type_object( 
  `Minimum Ad break length per TV show (seconds)` = ellmer::type_integer( 
    description = "Extract the minimum length of ads in seconds.
Rules:
1. If the text contains a numeric range 'X to Y seconds', set minimum = X.
2. If the text contains a numeric range 'X minutes', set minimum = X * 60.
3. If the text contains a single number 'X seconds', set minimum = X.
Examples:
- '75 to 105 seconds' → 75
- '3 minutes' → 180
- '75 seconds' → 75"
  ),
  `Maximum Ad break length per TV show (seconds)` = ellmer::type_integer( 
    description = "Extract the maximum length of ads in seconds.
Rules:
1. If the text contains a numeric range 'X to Y seconds', set maximum = Y.
2. If the text contains a numeric range 'X minutes', set maximum = X * 60.
3. If the text contains a single number 'X seconds', set maximum = X.
Examples:
- '75 to 105 seconds' → 105
- '3 minutes' → 180
- '75 seconds' → 75"
  )
)

# use the prompts and prompted list to clean the data 
# store in a new data frame table 
ad_length_tv_extracted <- ellmer::parallel_chat_structured(chat, prompts_tv_len, type = ad_break_length_tv) 


# store the fifth column of the dataframe as a list in prompts to be used with ellmer below
# this list will contain information about the ad break length during a movie
big_table[[5]] |> as.list() -> prompts_mov_len

# prompts for the chat to follow to separate the data into 2 columns: the minimum length of breaks during a movie, and the maximum length in seconds
ad_break_length_mov <- ellmer::type_object( 
  `Minimum Ad break length per movie (seconds)` = ellmer::type_integer( 
    description = "Extract the minimum length of ads in seconds.
Rules:
1. If the text contains a numeric range 'X to Y seconds', set minimum = X.
2. If the text contains a numeric range 'X minutes', set minimum = X * 60.
3. If the text contains a numeric range 'X minutes, Y seconds', set minimum = (X * 60) + Y.
4. If the text contains a single number 'X seconds', set minimum = X.
Examples:
- '75 to 105 seconds' → 75
- '3 minutes' → 180
- '75 seconds' → 75
- '2 minutes, 15 seconds' → 135
"
  ),
  `Maximum Ad break length per movie (seconds)` = ellmer::type_integer( 
    description = "Extract the maximum length of ads in seconds.
Rules:
1. If the text contains a numeric range 'X to Y seconds', set maximum = Y.
2. If the text contains a numeric range 'X minutes', set maximum = X * 60.
3. If the text contains a numeric range 'X minutes, Y seconds', set minimum = (X * 60) + Y.
4. If the text contains a single number 'X seconds', set maximum = X.
Examples:
- '75 to 105 seconds' → 105
- '3 minutes' → 180
- '75 seconds' → 75
- '2 minutes, 15 seconds' → 135
"
  )
)

# use the prompts and prompted list to clean the data 
# store in a new data frame table 
ad_length_mov_extracted <- ellmer::parallel_chat_structured(chat, prompts_mov_len, type = ad_break_length_mov) 
```



```{r Ads per title}

# store the sixth column of the dataframe as a list in prompts to be used with ellmer below
# this list will contain information about the length of all ads during an episode
big_table[[6]] |> as.list() -> prompts_title_tv


# prompts for the chat to follow to separate the data into 2 columns: the minimum length of ads during an episode, and the maximum length in minutes 
ad_title_tv <- ellmer::type_object( 
  `Minimum Ads per TV episode (minutes)` = ellmer::type_integer( 
    description = "Extract the minimum ad length in minutes
Rules:
1. If the text contains a numeric range 'X to Y minutes', set minimum = X.
Examples:
- '4 to 10 minutes' → 4
- '2 to 5 minutes' → 2
"
  ),
  `Maximum Ads per TV episode (minutes)` = ellmer::type_integer( 
    description = "Extract the maximum ad length in minutes
Rules:
1. If the text contains a numeric range 'X to Y minutes', set maximum = Y.
Examples:
- '4 to 10 minutes' → 10
- '2 to 5 minutes' → 5
"
  )
)

# use the prompts and prompted list to clean the data 
# store in a new data frame table 
ad_title_tv_extracted <- ellmer::parallel_chat_structured(chat, prompts_title_tv, type = ad_title_tv) 



# store the sixth column of the dataframe as a list in prompts to be used with ellmer below
# this list will contain information about the length of all ads during a movie
big_table[[7]] |> as.list() -> prompts_title_mov


# prompts for the chat to follow to separate the data into 2 columns: the minimum length of ads during a movie, and the maximum length in minutes  
ad_title_mov <- ellmer::type_object( 
  `Minimum Ads per movie (minutes)` = ellmer::type_integer( 
    description = "Extract the minimum ad length in minutes
Rules:
1. If the text contains a numeric range 'X to Y minutes', set minimum = X.
2. If the text contains a numeric 'X minutes', set minimum = X.
Examples:
- '4 to 10 minutes' → 4
- '2 to 5 minutes' → 2
"
  ),
  `Maximum Ads per movie (minutes)` = ellmer::type_integer( 
    description = "Extract the maximum ad length in minutes
Rules:
1. If the text contains a numeric range 'X to Y minutes', set maximum = Y.
2. If the text contains a numeric 'X minutes', set maximum = X.
Examples:
- '4 to 10 minutes' → 10
- '2 to 5 minutes' → 5
"
  )
)

# store the sixth column of the dataframe as a list in prompts to be used with ellmer below
# this list will contain information about the length of all ads during a movie
ad_title_mov_extracted <- ellmer::parallel_chat_structured(chat, prompts_title_mov, type = ad_title_mov) 
```


```{r}
# combine all of the extracted dataframes into one large table
platform_extraction <- bind_cols(big_table[1], ad_title_mov_extracted, ad_title_tv_extracted, ad_length_mov_extracted, ad_length_tv_extracted, mov_breaks_extracted, ep_breaks_extracted)
```


## Scraping Share of total U.S. TV viewing and household data from Adwave

```{r}

# Verify that the Adwave site allows web scraping for the path we wish to scrape
# A TRUE result allows web scraping
robotstxt::paths_allowed(
  paths = "resources/most-watched-streaming-service-q4-2025", 
  domain = "https://adwave.com"
  
)

# read the html into a variable
adwave_webpage <- rvest::read_html("https://adwave.com/resources/most-watched-streaming-service-q4-2025")

# using the saved html, find the text related to the streaming data
adwave_webpage |>
  rvest::html_elements("ul > li > p > b") |>
  rvest::html_text() -> streaming


# select only the data related to market share
streaming_mkt <- streaming[1:9]


# convert the data into a list to be used by the AI
streaming_mkt |> as.list() -> prompt_view_share

# generate prompting to clean the data into two columns: the platform name and the share written in decimal form
US_view_share <- ellmer::type_object( 
  `Platform` = ellmer::type_string( 
    description = "The streaming platform name.
Rules:
1. If the text contains (combined), follow the examples below.
2. If the text contains Streaming, follow the examples below.
3. Otherwise, report the written text as written. 
Examples:
- 'Disney (combined): 4.7%' → Disney+ and Hulu
- 'Paramount Streaming: 2.5%' → Paramount+
- 'Prime Video: 4.3%' → Prime Video
"
  ),
  `Share of total U.S. TV viewing (%)` = ellmer::type_number( 
    description = "Extract the share of total tv viewing.
Rules:
1. If the text contains a numeric value '2.5%', set viewing = 0.025.
2. Change the percentage to a decimal
Examples:
- 'Tubi: 2.0%' → 0.02
- 'Max: 1.8%' → 0.018
"
  )
)

# clean the data and save as a dataframe
TV_viewing_share <- ellmer::parallel_chat_structured(chat, prompt_view_share, type = US_view_share) 

```


```{r}

#select only the data related to households
household <- streaming[20:24]

# convert the data into a list to be used by the AI
household |> as.list() -> prompt_households

# generate prompting to clean the data and seperate into two columns: the platform name and the household penetration
household_reach_percent <- ellmer::type_object( 
  `Platform` = ellmer::type_string( 
    description = "The streaming platform name.
Examples:
- 'Disney+: 34%' → Disney+
- 'Amazon Prime Video: 67%' → Prime Video
"
  ),
  `U.S. household penetration (% of US households)` = ellmer::type_string( 
    description = "Extract the % of US households penetrated. 
    Rule: Change the percentage to a decimal.
Examples:
- 'Amazon Prime Video: 67%' → 0.67
"
  )
)

# clean the data and save as a dataframe
household_reach <- ellmer::parallel_chat_structured(chat, prompt_households, type = household_reach_percent) 

```


## Scraping global subscription data from ElectroIQ

```{r}

# Verify that the Adwave site allows web scraping for the path we wish to scrape
# A TRUE result allows web scraping
robotstxt::paths_allowed(
  paths = "/stats/streaming-services-statistics/", 
  domain = "https://electroiq.com"
  
)

# read the html into a variable
global_sub_webpage <- rvest::read_html("https://electroiq.com/stats/streaming-services-statistics/")

# use the saved html to select the tables on the page
global_sub_webpage |>
  rvest::html_elements("table") |>
  rvest::html_table() -> streaming_2

# streaming_2 contains 4 tibbles, one from each table on the site
# select the second to get information about the subscribers 
global_subs <- streaming_2[[2]]
# remove the columns related to Origin Country, Launch Year, and Served Country/Region
global_subs <- global_subs |> select(-c(X2,X3,X5))
# use the first row as the column names and remove the first row to include only the data in the dataframe 
colnames(global_subs) <- global_subs[1,]
global_subs <- global_subs[-1,]

# Select only the first 18 rows as these contain the most popular streaming sites
global_subs <- global_subs[1:18,]

# remove the "million" from the subscribers column and convert the values into decimals
global_subs$Subscribers <- as.numeric(gsub(" million", "", global_subs$Subscribers))

# rename the columns to be more descriptive and match other dataframes
global_subs <- global_subs |> rename("Platform" = "Service Name")
global_subs <- global_subs |> rename("Subscribers (Millions)" = "Subscribers")

```

## Final Cleaning and Merging Dataframes to Create the Final Dataset

```{r}

# Clean the data by relabeling streaming services that do not follow the traditional naming convention. 
# Rename to HBO Max
ott[5, "Platform"] <- "HBO Max"
platform_extraction[5, "Platform"] <- "HBO Max"
TV_viewing_share[8, "Platform"] <- "HBO Max"
watch_time[5, "Platform"] <- "HBO Max"

# Rename to Hulu TV
ott[11, "Platform"] <- "Hulu TV"

# Rename to Disney+
CAGR[2, "Platform"] <- "Disney+"

# Rename to Amazon Prime Video
platform_extraction[12, "Platform"] <- "Amazon Prime Video"
household_reach[3, "Platform"] <- "Amazon Prime Video"
TV_viewing_share[4, "Platform"] <- "Amazon Prime Video"
global_subs[6, "Platform"] <- "Amazon Prime Video"

# Rename to Discovery+
platform_extraction[2, "Platform"] <- "Discovery+"

# Rename to Paramount+
global_subs[13, "Platform"] <- "Paramount+"




# Join each dataframe into one large dataframe by matching rows with the same Platform name
master_set <- revenue |>
  full_join(ott,      by = "Platform") |>
  full_join(ad_spend, by = "Platform") |>
  full_join(CAGR,     by = "Platform") |> 
  full_join(household_reach,      by = "Platform") |>
  full_join(global_subs, by = "Platform") |>
  full_join(TV_viewing_share,     by = "Platform") |> 
  full_join(platform_extraction,     by = "Platform") |> 
  full_join(watch_time,     by = "Platform")



master_set
```

## Write the final dataset into a csv file

```{r}

write_csv(master_set, "C:\\Users\\rylee\\OneDrive\\Desktop\\401_data.csv")

```

